---
title: "My Notes"
author: "Eric Scott"
date: "2024-09-05"
format: 
  html: 
    toc: true
code-fold: true
bibliography: references.bib
---

## Load Data

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(palmerpenguins)
library(knitr)
```

We're using the `penguins` dataset from the `palmerpenguins` package [@palmerpenguins], so no loading of data is needed other than `library(palmerpenguins)`.

## Results

### Body Size

```{r}
#| warning: false 
#| code-fold: show
#| label: fig-box
#| fig-cap: "Boxplot of penguin body mass (in grams) by sex"
ggplot(penguins, aes(x = sex, y = body_mass_g)) + geom_boxplot()
```

As you can see in @fig-box, males are larger than females.
The sample sizes are roughly equal at all islands for males and females (@tbl-sample).
@dunn2016 also do some research with penguin size.

```{r}
#| label: tbl-sample
#| tbl-cap: "Sample sizes of penguins by sex and island"
kable(table(penguins$sex, penguins$island, useNA = "always"))
```

### Bill length

```{r}
#| label: fig-bill
#| fig-cap: "Bill length (mm) by sex" 

ggplot(penguins, aes(x = sex, y = bill_length_mm)) + geom_boxplot()
```

Males also have longer bills on average than females (@fig-bill).

$$
y = mx + b
$$ {#eq-line}

@eq-line shows the equation for a line with slope ($m$) and intercept ($b$)

## Escaping markdown

Use `\` as an "escape character" to stop symbols from doing anything special.

*itallics* vs \*literally surrounded with astrixes\*
